The Hyperedge Event Model

### 2019-01-19 paper/revision1/HEM-reply.tex
revised memo

@@

@@

\noindent  {\bf E9} \grey{\emph{The sampler usePs a blocked Gibbs sampler for the $u_{iej}$. Given the constraint that $\sum_j u_{iej} > 0$, this sampler may be rather inefficient in the case where there are many one-to-one interactions (as is the case in the application, where 83\% of the interactions are dyadic). In order to go from the state $u_{ie}$ = (1,0,0,0,0,0) to $u_{ie}$ = (0,1,0,0,0,0) one needs to go through a state where two receivers are activated, which has low probability in this case. It would be good to comment on this, and in general on the mixing of the MCMC sampler. }}\\

@@

@@

@@

@@

\noindent {\bf R4} \grey{\emph{As already mentioned, the authors focus on the somewhat less explored area of continuous?time relational event models where each edge has its own different time index?instead of considering time?varying models for snap- shots of networks collected on a pre?specified time grid. However, the contribution is still within the general class of dynamic network inference. In this respect, the literature review provides a poor picture for the state-of-the-art in this wider framework. I think the authors should provide a more comprehensive literature review including also temporal ERGMs and dynamic latent variable models (e.g. dynamic stochastic block models, dynamic mixed membership stochastic block models, dynamic latent space models, . . .). Discussing your contribution in the light of these alternative (and quite different) models would further clarify the key novelties our the proposed methods.}}\\

@@

\noindent {\bf R6} \grey{\emph{You present the full conditionals in page 7 assuming uninformative $N(0, \infty)$ priors, but then you rely on weakly informative priors in the application (see page 17). I found this confusing. I?d present results in page 7 for generic Gaussian priors.}}\\

@@

@@

@@

\noindent {\bf R11} \grey{\emph{In Figure 4c the choice of the logarithmic scale for MdAPE seems to hide a quite poor performance of your model in predicting the timestamps. It is true that the log?normal improves over the exponential, but the log?normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big. This is to me a negative result, which should be discussed and addressed in the paper.}}\\

>>>>

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor indicated lack of discussion on the relavent literature, including specific comparison between other papers we mentioned (e.g., Perry and Wolfe (2013) and Snijders (1996)). We created new section 2.4 ``Basis in existing models" which provides detailed summaries and comparisons about existing models that affected the HEM. Furthermore, we added more comments when we introduce/cite the papers with emphasis on what are the motivation and how our model uses differently.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor called attention to a very important point about conditional dependency that we were missing. Our out-of-sample algorithm (Algorithm 3) was not correct, and the conditional distribution for missing observations had to be changed as the Editor illustrated. We modified our algorithm to consider those dependencies, and Section 4.2 is fully updated based on new conditional distribution and experiment results. \\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor asked to provide more details on the proposals we used for the Metropolis-Hastings algorithm, thus we added further explanations for both parameters $b$ and $\eta$ in Section 3.1.\\

\noindent  {\bf E9} \grey{\emph{The sampler uses a blocked Gibbs sampler for the $u_{iej}$. Given the constraint that $\sum_j u_{iej} > 0$, this sampler may be rather inefficient in the case where there are many one-to-one interactions (as is the case in the application, where 83\% of the interactions are dyadic). In order to go from the state $u_{ie}$ = (1,0,0,0,0,0) to $u_{ie}$ = (0,1,0,0,0,0) one needs to go through a state where two receivers are activated, which has low probability in this case. It would be good to comment on this, and in general on the mixing of the MCMC sampler. }}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified some inefficiency issue in our inference algorithm, which we did not fully commented. Considering our general need to discuss more about our model's computational complexity, we generated new section 3.2 about ``computaional complexity" and left various comments including the usage of a blocked Gibbs sampler and the mixing of our MCMC sampler.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially since our application data is rather small, so (as mentioned in E9) we generated new section 3.2 about ``computaional complexity" and left comments on our computational limitation.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor identified numerous typos, and we properly fixed all those. \\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer dentified numerous typos, and we properly fixed all those.  \\

@@

\noindent {\bf R4} \grey{\emph{As already mentioned, the authors focus on the somewhat less explored area of continuous-time relational event models where each edge has its own different time index, instead of considering time-varying models for snap-shots of networks collected on a pre-specified time grid. However, the contribution is still within the general class of dynamic network inference. In this respect, the literature review provides a poor picture for the state-of-the-art in this wider framework. I think the authors should provide a more comprehensive literature review including also temporal ERGMs and dynamic latent variable models (e.g. dynamic stochastic block models, dynamic mixed membership stochastic block models, dynamic latent space models, . . .). Discussing your contribution in the light of these alternative (and quite different) models would further clarify the key novelties our the proposed methods.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer indicated lack of discussion on our model's contribution on the general class of dynamic network literature, specifically in lights of temporal ERGMs and dynamic latent variable models. We created new section 2.4 ``Basis in existing models" which provides detailed summaries on our contribution and comparisons with other existing models in wider framework. \\

@@

\noindent {\bf R6} \grey{\emph{You present the full conditionals in page 7 assuming uninformative $N(0, \infty)$ priors, but then you rely on weakly informative priors in the application (see page 17). I found this confusing. I'd present results in page 7 for generic Gaussian priors.}}\\

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested to use generic Gaussian priors in page 7, instead of introducing the full conditionals assuming uninformative $N(0, \infty)$ priors. We addressed this issue by assuming generic Normal priors $N(\mu, \Sigma)$ for both $b$ and $\eta$ and revised our equations and corresponding explanations in page 7.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The reviewer suggested more sensitivity analyses on hyperparameter specification. We tried two alternative specification of prior distribution---one with half size of current variance and another with double size of current variance--- and summarized the results in Appendix. Also, we left some comments on these settings in Section 3.2.\\

@@

\noindent \textcolor{MyGreen}{\textbf{Addressed:}} The Editor suggested more detailed explanation on the computational complexity, especially because we had slow mixing of MCMC samples and thus end up with large thinning. We generated new section 3.2 about ``computaional complexity" and left comments on our computational limitations, including poor mixing of data augmentation.\\

@@

\noindent {\bf R11} \grey{\emph{In Figure 4c the choice of the logarithmic scale for MdAPE seems to hide a quite poor performance of your model in predicting the timestamps. It is true that the log?normal improves over the exponential, but the log-normal boxplot has still a third quartile providing an MdAPE of exp(7.36) which looks quite big. This is to me a negative result, which should be discussed and addressed in the paper.}}\\
